ITS\_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space

### 2023-10-31 paper.qmd
fix figure 1 refs

⏹️  Earth Science is being upended by advancements in cloud computing technology, an explosion in remote sensing data collection (Fig. 1), and a cultural shift toward open science. The global satellite data record has grown too large to be downloaded and analyzed on personal computers, machine-learning algorithms have grown too complex to be maintained by any single research group, and there is a growing recognition that public investments in research are compounded when code is open. 
NASA is embracing the new paradigm, and is moving all Earth observation data archives into Earthdata cloud https://www.earthdata.nasa.gov/eosdis/cloud-evolution as part of the Transform to Open Science initiative https://nasa.github.io/Transform-to-Open-Science/. Here we show how NASA's MEaSUREs program is pushing Earth Science into the cloud computing era with automated production, open code, intelligent cloud-optimized data products, single-line-of-code data access and subsetting, and no-code, user-friendly interfaces for data exploration and visualization as developed for the ITS_LIVE project https://its-live.jpl.nasa.gov.

@@

ITS_LIVE data processing uses a cloud-first approach to minimize downloading of data and to optimize for rapid data access and large-scale analysis. Dataset generation is carried out in Amazon AWS using [HyP3 @Hogenson2023-cj] , scaling to >10,000 cores. HyP3 is an open-source, cloud-native batch processing pipeline developed by the Alaska Space Facility for processing optical and Synthetic Aperture Radar (SAR) imagery that addresses many common issues for users of SAR data. Most analysis code is run in the US-West-2 region where the majority of the imagery is archived while the Sentinel-2 processing is run in EU-Central-1.

@@

ITS_LIVE provides users with intuitive no-code options to explore the rich dataset through a Voila-based dashboard and a serverless application [Fig 5].. In the following pages we present some of the data visualizations we can obtain from using ITS_LIVE data without costly pre-processing steps using open-source GIS tools like QGIS[8] and the Pangeo stack in Python ([Xarray @Hoyer2017-su], [Zarr @Miles2023-yj] , [HoloViews @Rudiger2020-yr]). A companion GitHub repository contains all the notebooks and QGIs projects used to generate the figures in this article. The focus areas include Malaspina Glacier in Alaska (Fig. 4,7), Pine Island Glacier in Antarctica and Antarctic ice shelves (Fig. 6)

@@

![](figures/figure-1-full.jpg)

>>>>

⏹️  Earth Science is being upended by advancements in cloud computing technology, an explosion in remote sensing data collection (@fig-1), and a cultural shift toward open science. The global satellite data record has grown too large to be downloaded and analyzed on personal computers, machine-learning algorithms have grown too complex to be maintained by any single research group, and there is a growing recognition that public investments in research are compounded when code is open. 
NASA is embracing the new paradigm, and is moving all Earth observation data archives into Earthdata cloud https://www.earthdata.nasa.gov/eosdis/cloud-evolution as part of the Transform to Open Science initiative https://nasa.github.io/Transform-to-Open-Science/. Here we show how NASA's MEaSUREs program is pushing Earth Science into the cloud computing era with automated production, open code, intelligent cloud-optimized data products, single-line-of-code data access and subsetting, and no-code, user-friendly interfaces for data exploration and visualization as developed for the ITS_LIVE project https://its-live.jpl.nasa.gov.

@@

ITS_LIVE data processing uses a cloud-first approach to minimize downloading of data and to optimize for rapid data access and large-scale analysis. Dataset generation is carried out in Amazon AWS using [HyP3 @Hogenson2023-cj] , scaling to >10,000 cores. HyP3 is an open-source, cloud-native batch processing pipeline developed by the Alaska Satellite Facility for processing optical and Synthetic Aperture Radar (SAR) imagery that addresses many common issues for users of SAR data. Most analysis code is run in the US-West-2 region where the majority of the imagery is archived while the Sentinel-2 processing is run in EU-Central-1.

@@

ITS_LIVE provides users with intuitive no-code options to explore the rich dataset through a Voila-based dashboard and a serverless application [Fig. @fig-3] In the following pages we present some of the data visualizations we can obtain from using ITS_LIVE data without costly pre-processing steps using open-source GIS tools like QGIS[8] and the Pangeo stack in Python ([Xarray @Hoyer2017-su], [Zarr @Miles2023-yj] , [HoloViews @Rudiger2020-yr]). A companion GitHub repository contains all the notebooks and QGIs projects used to generate the figures in this article. The focus areas include Malaspina Glacier in Alaska (@fig-2;@fig-5), Pine Island Glacier in Antarctica and Antarctic ice shelves (@fig-4)

@@

![](figures/figure-1-consolidated.jpg)

### 2023-10-31 paper.tex
fix figure 1 refs

\affiliation[1]{organization={NSIDC, University of Colorado
Boulder},,postcodesep={}}
\affiliation[2]{organization={NASA, Jet Propulsion
Laboratory},,postcodesep={}}
\affiliation[3]{organization={UAF, Geophysical
Institute},,postcodesep={}}
\affiliation[4]{organization={UAF, Alaska Satellite
Facility},,postcodesep={}}
\affiliation[5]{organization={CIRES, Earth Science and Observation
Center},,postcodesep={}}
\affiliation[6]{organization={Wentworth Institute of
Technology},,postcodesep={}}

@@

\begin{keyword}
    glaciology \sep climate change \sep big data \sep 
    cloud computing
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners]}{\end{tcolorbox}}\fi

@@

⏹️ Earth Science is being upended by advancements in cloud computing
technology, an explosion in remote sensing data collection (Fig. 1), and
a cultural shift toward open science. The global satellite data record
has grown too large to be downloaded and analyzed on personal computers,
machine-learning algorithms have grown too complex to be maintained by
any single research group, and there is a growing recognition that
public investments in research are compounded when code is open. NASA is
embracing the new paradigm, and is moving all Earth observation data
archives into Earthdata cloud
https://www.earthdata.nasa.gov/eosdis/cloud-evolution as part of the
Transform to Open Science initiative
https://nasa.github.io/Transform-to-Open-Science/. Here we show how
NASA's MEaSUREs program is pushing Earth Science into the cloud
computing era with automated production, open code, intelligent
cloud-optimized data products, single-line-of-code data access and
subsetting, and no-code, user-friendly interfaces for data exploration
and visualization as developed for the ITS\_LIVE project
https://its-live.jpl.nasa.gov.

@@

ITS\_LIVE data processing uses a cloud-first approach to minimize
downloading of data and to optimize for rapid data access and
large-scale analysis. Dataset generation is carried out in Amazon AWS
using \citep[HyP3][]{Hogenson2023-cj} , scaling to \textgreater10,000
cores. HyP3 is an open-source, cloud-native batch processing pipeline
developed by the Alaska Space Facility for processing optical and
Synthetic Aperture Radar (SAR) imagery that addresses many common issues
for users of SAR data. Most analysis code is run in the US-West-2 region
where the majority of the imagery is archived while the Sentinel-2
processing is run in EU-Central-1.

@@

ITS\_LIVE provides users with intuitive no-code options to explore the
rich dataset through a Voila-based dashboard and a serverless
application {[}Fig 5{]}.. In the following pages we present some of the
data visualizations we can obtain from using ITS\_LIVE data without
costly pre-processing steps using open-source GIS tools like QGIS{[}8{]}
and the Pangeo stack in Python (\citep[Xarray][]{Hoyer2017-su},
\citep[Zarr][]{Miles2023-yj} , \citep[HoloViews][]{Rudiger2020-yr}). A
companion GitHub repository contains all the notebooks and QGIs projects
used to generate the figures in this article. The focus areas include
Malaspina Glacier in Alaska (Fig. 4,7), Pine Island Glacier in
Antarctica and Antarctic ice shelves (Fig. 6)

\pagebreak

@@

\includegraphics{figures/figure-1-full.jpg}

@@

\textbf{ACKNOWLEDGMENTS}

The ITS\_LIVE user community for their helpful feedback. Pangeo
community. Copernicus Sentinel data processed by ESA. Landsat data
courtesy of the U.S. Geological Survey. Funding for ITS\_LIVE provided
by the NASA MEaSUREs program.

>>>>

\affiliation[1]{organization={NSIDC, University of Colorado
Boulder},,postcodesep={}}
\affiliation[2]{organization={NASA, Jet Propulsion Laboratory,
California Institute of Technology},,postcodesep={}}
\affiliation[3]{organization={UAF, Geophysical
Institute},,postcodesep={}}
\affiliation[4]{organization={UAF, Alaska Satellite
Facility},,postcodesep={}}
\affiliation[5]{organization={CIRES, Earth Science and Observation
Center},,postcodesep={}}
\affiliation[6]{organization={Wentworth Institute of
Technology},,postcodesep={}}

@@

\begin{keyword}
    glaciology \sep climate change \sep big data \sep 
    cloud computing
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, breakable, sharp corners, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

⏹️ Earth Science is being upended by advancements in cloud computing
technology, an explosion in remote sensing data collection
(Figure~\ref{fig-1}), and a cultural shift toward open science. The
global satellite data record has grown too large to be downloaded and
analyzed on personal computers, machine-learning algorithms have grown
too complex to be maintained by any single research group, and there is
a growing recognition that public investments in research are compounded
when code is open. NASA is embracing the new paradigm, and is moving all
Earth observation data archives into Earthdata cloud
https://www.earthdata.nasa.gov/eosdis/cloud-evolution as part of the
Transform to Open Science initiative
https://nasa.github.io/Transform-to-Open-Science/. Here we show how
NASA's MEaSUREs program is pushing Earth Science into the cloud
computing era with automated production, open code, intelligent
cloud-optimized data products, single-line-of-code data access and
subsetting, and no-code, user-friendly interfaces for data exploration
and visualization as developed for the ITS\_LIVE project
https://its-live.jpl.nasa.gov.

@@

ITS\_LIVE data processing uses a cloud-first approach to minimize
downloading of data and to optimize for rapid data access and
large-scale analysis. Dataset generation is carried out in Amazon AWS
using \citep[HyP3][]{Hogenson2023-cj} , scaling to \textgreater10,000
cores. HyP3 is an open-source, cloud-native batch processing pipeline
developed by the Alaska Satellite Facility for processing optical and
Synthetic Aperture Radar (SAR) imagery that addresses many common issues
for users of SAR data. Most analysis code is run in the US-West-2 region
where the majority of the imagery is archived while the Sentinel-2
processing is run in EU-Central-1.

@@

ITS\_LIVE provides users with intuitive no-code options to explore the
rich dataset through a Voila-based dashboard and a serverless
application Fig.~\ref{fig-3} In the following pages we present some of
the data visualizations we can obtain from using ITS\_LIVE data without
costly pre-processing steps using open-source GIS tools like QGIS{[}8{]}
and the Pangeo stack in Python (\citep[Xarray][]{Hoyer2017-su},
\citep[Zarr][]{Miles2023-yj} , \citep[HoloViews][]{Rudiger2020-yr}). A
companion GitHub repository contains all the notebooks and QGIs projects
used to generate the figures in this article. The focus areas include
Malaspina Glacier in Alaska (Figure~\ref{fig-2};Figure~\ref{fig-5}),
Pine Island Glacier in Antarctica and Antarctic ice shelves
(Figure~\ref{fig-4})

@@

\includegraphics{figures/figure-1-consolidated.jpg}

@@

\textbf{Acknowledgments}

\begin{itemize}
\tightlist
\item
  The ITS\_LIVE user community for their helpful feedback.
\item
  Pangeo community.
\item
  Copernicus Sentinel data processed by ESA.
\item
  Landsat data courtesy of the U.S. Geological Survey.
\item
  Funding for ITS\_LIVE provided by the NASA MEaSUREs program.
\item
  A portion of this work was conducted at the Jet Propulsion Laboratory,
  California Institute of Technology, under contract with the National
  Aeronautics and Space Administration ©2023 All rights reserved.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
